A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Supplementary Material

### 2018-11-23 MS.tex
Read up until `Comparison of longevity estimates from two methods'

Dissection allows the number of completed gonotrophic cycles to be
counted and from this the mean number of cycles before death was
estimated. Overall, the mean number of cycles completed in a lifetime
was 1.2 (Fig. \ref{fig:dissection_lifetimes_exponential}; posterior median) and across the 131 studies, 95\% of
the individual time series estimates were less than 3 (Fig. \ref{fig:dissection_individualEstimates_allSpecies}). The
estimated greatest number of cycles was for \emph{Anopheles sergentii}
(2.5 cycles; posterior median) which is adapted to desert conditions (it
is known as the ``oasis vector'' of malaria) and may have evolved
greater longevity. The important African malaria vector \emph{An.
gambiae s.l.} was estimated to be the second longest living (1.9 cycles;
posterior median). The smallest estimated mean number of gonotrophic
cycles was for \emph{Anopheles} \emph{bellator} (0.5 cycles; posterior
median) which transmits malaria in Brazil's Atlantic Forest. There were
significant differences in estimated lifetime gonotrophic cycles amongst
species (ANOVA: \emph{F}\textsubscript{24,106} =2.2, \emph{p}
\textless{}0.01; the non-parametric Kruskal Wallace:
\({\chi^{2}}_{24}\), \emph{p}\textless{}0.01).

The estimated lifetime gonotrophic cycles for the different genera were
\emph{Anopheles,} 1.4; \emph{Mansonia}, 1.1; \emph{Culex,} 1.0; and
\emph{Aedes} 0.8 (Fig. \ref{fig:dissection_lifetimes_exponential}) and the differences between the genera were
significant (ANOVA: \emph{F}\textsubscript{3,127} =3.4, \emph{p} =0.02;
the non-parametric Kruskal Wallace: \(\chi_{3}^{2} = 21.7\),
\emph{p}\textless{}0.01).

>>>>

Dissection allows the number of completed gonotrophic cycles to be
counted and from this the mean number of cycles before death was
estimated. Overall, the mean number of cycles completed in a lifetime
was 1.3 (posterior mean; Fig. \ref{fig:dissection_lifetimes_exponential}; Table S\ref{S-tab:dissection_estimated_lifespans}) and across the 131 studies, 95\% of
the individual time series estimates were less than 3 (Fig. \ref{fig:dissection_individualEstimates_allSpecies}). The
estimated greatest number of cycles was for \emph{Anopheles sergentii}
(3.0 cycles; posterior mean) which is adapted to desert conditions (it
is known as the ``oasis vector'' of malaria) and may have evolved
greater longevity. The important African malaria vector \emph{A.
gambiae s.l.} was estimated to be the second longest living (2.4 cycles;
posterior mean). The smallest estimated mean number of gonotrophic
cycles was for \emph{Anopheles} \emph{bellator} (0.6 cycles; posterior
mean) which transmits malaria in Brazil's Atlantic Forest. There were
significant differences in estimated lifetime gonotrophic cycles amongst
species (ANOVA: \emph{F}\textsubscript{24,106} =2.2, \emph{p}
\textless{}0.01; the non-parametric Kruskal Wallace:
\({\chi^{2}}_{24}\), \emph{p}\textless{}0.01).

The estimated lifetime gonotrophic cycles for the different genera were
\emph{Anopheles,} 1.6; \emph{Culex,} 1.2; \emph{Mansonia}, 1.1; and
\emph{Aedes} 0.8 (Fig. \ref{fig:dissection_lifetimes_exponential}; Table S\ref{S-tab:dissection_estimated_lifespans}) and the differences between the genera were
significant (ANOVA: \emph{F}\textsubscript{3,127} =3.4, \emph{p} =0.02;
the non-parametric Kruskal Wallace: \(\chi_{3}^{2} = 21.7\),
\emph{p}\textless{}0.01).
